---
title: "simulation part 2"
author: "Shaaguunz"
date: "5/18/2020"
output: html_document
---


**Questions**
Now in the second portion of the project, we're going to analyze the ToothGrowth data in the R datasets package.

Load the ToothGrowth data and perform some basic exploratory data analyses
Provide a basic summary of the data.
Use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose. (Only use the techniques from class, even if there's other approaches worth considering)
State your conclusions and the assumptions needed for your conclusions.


**Load the data**
```{r}
library(ggplot2)
data("ToothGrowth")
```


1.  summary of data

```{r}
head(ToothGrowth)
```

types of supplemennts and dosages

```{r}
table(ToothGrowth$supp)
table(ToothGrowth$dose)
```

summary of ToothGrowth

```{r}
summary(ToothGrowth)

```

Correlation in ToothGrowth Data
```{r}
cor(ToothGrowth[sapply(ToothGrowth,is.numeric)])
```

so length and dosage have high correlation

**Plotting**
```{r}
plt1<-ggplot(ToothGrowth,aes(x=factor(dose),y=len,fil=factor(dose)))
plt1+geom_boxplot()+xlab("Dosage")+ylab("Length")

```


2.  Use confidence intervals and hypothesis tests to compare tooth growth by supp and dose

95% interval
```{r}
Interval<-(mean(ToothGrowth$len)+c(-1,1)*qnorm(0.975)*sd(ToothGrowth$len)/sqrt(length(ToothGrowth$len)))
Interval
```

T test by length and supplement

```{r}
t.test(len~supp,data=ToothGrowth)

```

so we cannot reject the null hypothesis

T test of dosage level

```{r}
dos1<-subset(ToothGrowth,dose==0.5)
dos2<-subset(ToothGrowth,dose==1)
dos3<-subset(ToothGrowth,dose==2)


t.test(len~supp,data=dos1)
t.test(len~supp,data=dos2)
t.test(len~supp,data=dos3)

```


for small and medium their p -values are small so we can reject the null hypothesis
however fo big dosage we cannot reject the null hypothesis 



3.   State your conclusions and the assumptions needed for your conclusions.


The tooth length growth is not controlled by supplements

For dosage level  0.5 and 1,  the Orange Juice has a higher effect on the length of tooth of Guinea Pigs than the Vitamin C.


For dosage level 2, there are so such difference between Orange Juice and Vitamin C